Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2020-06-07 analysis/drought/explore_prec_longterm.Rmd
new versions

---
title: "LongTerm Hydrological Prec"
author: "AJ Perez-Luque (@ajpelu)"
output: 
  md_document:
    variant: markdown_github
bibliography: ../references.bib 
csl: ../ecology.csl
---

@@

>>>>

---
title: "LongTerm Hydrological Prec"
author: "AJ Perez-Luque (@ajpelu)"
output: 
  md_document:
    variant: markdown_github
bibliography: ../references.bib 
csl: ../ecology.csl
editor_options: 
  chunk_output_type: console
---

@@

aux_SJ <- aux %>% filter(code %in% c("5501","5502","5504","5504A","5505","5509","5509A")) %>% mutate(site = "SJ")
aux_CA <- aux %>% filter(code %in% c("6242U","6243E","6248","6257")) %>% mutate(site = "CA")

prec_sites <- aux_SJ %>% bind_rows(aux_CA)

prec_sites_mean <- prec_sites %>% 
  dplyr::select(-code) %>% 
  group_by(hyear, site) %>% 
     dplyr::summarise(
     csum_mean = mean(csum, na.rm = TRUE),
     csum_sd = sd(csum, na.rm = TRUE), 
     csum_se = csum_sd/sqrt(length(csum_sd)), 
     n = n())

pos <- position_dodge(width = .9)

prec_sites_mean %>% filter(hyear > 1990) %>% 
  ggplot(aes(x=hyear, y=csum_mean, fill=site, colour = site)) + 
  geom_line(position = pos) +
  # geom_hline(yintercept = meandf) + 
  # geom_hline(yintercept = meandf + 2*sddf, color ='blue', linetype = 'dashed') +
  # geom_hline(yintercept = meandf - 2*sddf, color ='red', linetype = 'dashed') +
  # geom_hline(yintercept = meandf + 1*sddf, color ='blue', linetype = 'dotted') +
  # geom_hline(yintercept = meandf  - 1*sddf, color ='red', linetype = 'dotted') +
  scale_x_continuous(breaks=seq(1990,2020, by=5)) +
  scale_y_continuous(breaks=seq(0,1500, by=250)) +
  geom_errorbar(aes(ymin = csum_mean - csum_se, ymax= csum_mean + csum_se), width=.1, position = pos) +
  geom_point(size=2, position = pos) + theme_bw() + 
  theme(panel.grid.minor = element_blank()) +
  ylab('Cumulative Precipitation (hydrological year)') + xlab('year')

6257I
6242U
6236
```

### 2020-06-07 man/figures/0_figures_ecosystems.Rmd
new versions

@@

>>>>

**Figure S7.** Schema of the metrics (*a*) and analysis (*b*) used in the manuscript (see Material and methods for details) and their relation with the aims (numbers in grey circles) of our study (see Introduction). The severe drought events since 1901 were identified using SPEI-12 and regional climatic data. They were characterized in terms of duration, severity, intensity. Resilience metrics of BAI were computed for the most severe drought events since 1950, and the relationship of them to the severity of the drought were explored. For 2005 and 2012 drought events we also compute resilience metrics. A comparison of EVI and BAI resilience metrics for the 2005 and 2012 drought events was conducted among Q. pyrenaica populations.

@@

#####
**Figure S7**
![](../../man/figures/schema_methods/propuesta_esquema2.jpg)
